Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-23 output/latex/manuscript.tex
update reference to Zenodo archive

All the main datasets generated in this study are available at \url{https://doi.org/10.5281/zenodo.8044955}\textsuperscript{\protect\hyperlink{ref-Bf2hvBbr}{116}} and the GitHub repository \url{https://github.com/greenelab/phenoplier}.

@@

The code necessary to reproduce all the analyses in this work is available at \url{https://doi.org/10.5281/zenodo.8044955}\textsuperscript{\protect\hyperlink{ref-Bf2hvBbr}{116}} and the GitHub repository \url{https://github.com/greenelab/phenoplier}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Bf2hvBbr}{}}%
\CSLLeftMargin{116. }%
\CSLRightInline{Pividori, M. \& Greene, C. \emph{greenelab/phenoplier: Improvements in the source code}. (Zenodo, 2023). doi:\href{https://doi.org/10.5281/zenodo.8044956}{10.5281/zenodo.8044956}.}

>>>>

All the main datasets generated in this study are available at \url{https://doi.org/10.5281/zenodo.8071382}\textsuperscript{\protect\hyperlink{ref-cygmsEBt}{116}} and the GitHub repository \url{https://github.com/greenelab/phenoplier}.

@@

The code necessary to reproduce all the analyses in this work is available at \url{https://doi.org/10.5281/zenodo.8071382}\textsuperscript{\protect\hyperlink{ref-cygmsEBt}{116}} and the GitHub repository \url{https://github.com/greenelab/phenoplier}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-cygmsEBt}{}}%
\CSLLeftMargin{116. }%
\CSLRightInline{Pividori, M. \& Greene, C. \emph{greenelab/phenoplier: a computational framework to integrate genetic studies with gene co-expression patterns}. (Zenodo, 2023). doi:\href{https://doi.org/10.5281/zenodo.8071382}{10.5281/zenodo.8071382}.}
